The effect of detector nonlinearity on \wfa\ PSF profiles for weak gravitational lensing measurements

### 2016-01-19 bias_from_NL.tex
Added Chaz's suggestions

\newcommand {\gs} {{\tt{GalSim}}}  
\newcommand {\wf} {WFIRST}  
\newcommand {\wfa} {WFIRST-AFTA}  
\newcommand {\optical} {{\tt{OpticalPSF}}} 
\newcommand {\gauss} {{\tt{Gaussian}}}

@@

\title{Voltage non-linearity effects on \wfa\ PSF profiles for weak lensing measurements using {\tt{GalSim}} simulations}
\author{A. A. Plazas$^{\dagger a}$, C. Shapiro$^a$, J. Rhodes$^a$, \& R. Smith$^b$}
\email{$^\dagger$andres.a.plazas.malagon@jpl.nasa.gov}
\affil{$^a$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA 91109, USA}
\affil{$^b$Caltech Optical Observatories, 1200 E. California Blvd, MC11-17, CA 91125, USA}
\begin{abstract}
Weak gravitational lensing (WL) is one of the most powerful techniques to learn about the dark sector of the universe. To extract the WL signal from astronomical observations, observed galaxy shapes must be measured and corrected for the Point Spread Function (PSF) of the imaging system with extreme accuracy (of the order of 1 part per 1000). Future missions such as NASA's Wide Field Infrared Survey Telescope-Astrophysics Focused Telescope Asset (\wfa) will use a new family of hybrid near-infrared CMOS detectors that can potentially bias WL measurements. In particular, these detectors are intrinsically subject to non-linearities in the conversion of photo-generated charge to measured voltage that tend to attenuate bright objects such as reference stars that are used for PSF determination. In this paper, we study the impact on \wf\ PSF properties (size and ellipticity) induced by this type of signal-dependent voltage non-linearity (VNL). We use the publicly-available \gs\ and the \wf\ Exposure Time Calculator codes to generate customized simulations of the PSF optical profiles expected for \wf\ and study the consequences of a one-parameter non-linearity function quadratic in the signal $Q$ (in electrons) per pixel, $f(Q)=Q-\beta Q^2$. We use these simulations to measure the fractional error in the PSF size ($\Delta R/R$) and the absolute error in the PSF ellipticity ($\Delta e$) as a function of parameters such as the expected magnitude of typical stars in \wf\ and  $\beta$. For a measured nominal $\beta_0=3.566\times10^{-7}/e^{-}$, VNL attenuates the signal by about $3.5\%$ per each $10^5$ e$^-$ input. We find that the effect of VNL is chromatic in the four bands of the High Latitude Survey (HLS) of \wf\, and that its amplitude is the largest for the J129 band. As $\beta$ is allowed to increase, the values of $\Delta R/R$ and $\Delta e$ increase linearly in all bands at a fixed magnitude. We find that if not corrected, VNL at its nominal value can induce an error of $\Delta R/R=5\times 10^{-3}$ and $\Delta e_2=10^3$ in the \wf\ PSF size and ellipticity in the J129 bandpass for the expected brightest stars in the High Latitude Survey of \wf. In addition, or simulations show that to limit the bias of $\Delta R/R$ and $\Delta e$ in the J129 band to better than 1 part in 1000, $\beta$ must be calibrated to $\sim3\%$ and $\sim 6\%$, respectively.  
\end{abstract}

\section{Introduction}
Weak gravitational lensing (WL) has been identified as a powerful probe of the nature and evolution of the components of the Universe. In particular, \emph{cosmic shear}-the subtle  distortions of background galaxy shapes by the large scale structure of the Universe-constrains the properties of dark matter and dark energy through the measurement of the expansion history and growth of structure of the Universe\citep{refregier03, hoekstra08, kilbinger15}. In addition, WL measurements allow to test the validity of General Relativity that relates the gravitational potential to the matter-energy distribution. Several visible and near-infra red (NIR) surveys of $>1000$~deg$^2$ of the sky are currently underway and use the WL signal from hundreds of millions of galaxies as one of their central scientific techniques (\emph{e.g.}, the Dark Energy Survey (DES) \citep{diehl12,jarvis15}, the the Kilo-Degree Survey (KiDS) \citep{kuijken15}, and the Hypersuprime-Camera Survey (HSC)\citep{miyazaki12}. In addition, future ground- and spaced-based surveys and missions are planned to image more than O($10^9$) galaxies in the next decade (\emph{e.g.}, the Large Synoptic Survey Telescope (LSST) \citep{ivezic08}, the Euclid spacecraft \citep{laureijs11} and  NASA's planned Wide Field Infrared Survey Telescope (WFIRST) in its Astrophysics Focused Telescope Asset (AFTA) implementation \citep{green12,spergel13,spergel15}).

The process of extracting the WL signal from images of the sky, in the presence of intrinsic galaxy ellipticity variations are $\sim$ 0.4 r.m.s, is highly non-trivial. It must be done through an statistical analysis of large galaxy samples, with a careful control of systematic uncertainties. The dominant signal produced by WL can be described by a local linear transformation of the source image that produces a shear (a complex, spin-2 field of components $\gamma_1$ and $\gamma_2$) and a scalar magnification, both of which have an r.m.s. amplitude of only $\sim 2 \%$ in the case of cosmic shear. Most of the background galaxies usable by WL are at hight redshift (with low signal-to-noise (S/N) ratio) and with a size comparable or smaller than the Point Spread Function (PSF) of the imaging system. The PSF itself is usually larger than the lensing signal by an order of magnitude, inducing a modulation in the signal (multiplicative errors) and asymmetries that produce coherent spurious patterns (additive errors) that mimmic the WL signal. Bright stars are commonly used to estimate the PSF function, and then this information must be interpolated to the observed galaxy positions to deconvolve the PSF contribution and measure the galaxy shape (in the form of a complex ellipticity $e=e_1 + i e_2$) to estimate the shear field\footnote{Most of the shape measurement algorithms to date rely on the accurate measurements of galaxy shapes to produce an estimator of the WL shear field $(\gamma_1, \gamma_2)$. However, recent algorithms propose skipping this step and creating a direct shear estimator through Bayesian analysis in Fourier space \citep{bernstein14,bernstein15})}. This interpolation step is subject to introduce systematic errors if the information inferred from the stars does not fully constrain the PSF at the galaxy position with the required accuracy.  In order not to bias the determination of cosmological parameters and dark energy, the ellipticity and size of the PSF must be known to an accuracy of O(10$^{-3}$) \citep{huterer06,amara08,paulin08,paulin09,massey13,cropper13} or better ($4.7 \times 10^{-4}$ for the knowledgement of the \wfa\ PSF ellipticity  \citep{spergel13}).

@@

Systematic errors that originate from the photon detectors can also introduce biases in astronomical observables such as photometry and astrometry that propagate into shear measurement biases. These type of errors have been extensively studied in the case of thick, fully-depleted, high-resistivity CCDs, which are the detectors of choice for many current and planned surveys such as DES, HSC, and LSST \citep{stubbs14,plazas14,gruen15}. It is of great importance to qualitatively quantify the impact of these sensor effects on the inference of cosmological parameter, in particular through WL \citep{jarvis14,mandelbaum14b,meyers14}. Future missions such as the James Webb Space Telescope and \wfa\ will utilize a new family of near-infrared detectors that are subject as well to effects such as non-linearity, reciprocity failure \citep{biesiadzinski11}, interpixel capacitance (IPC) \citep{mccullough08,kannawadi15}, and persistence\citep{smith08}, and that can potentially imprint biases on weak lensing shape measurements if not taken into account.

In this paper we study the effect on PSF size and ellipticity of the non-linearity in the conversion of photo-generated charge to measured voltages in the NIR detectors that will be used by NASA's \wfa\ mission. This voltage non-linearity (VNL) will tend to attenuate the flux in bright stars, broadening the PSF and complicating the deconvolution of the PSF from the observed galaxy image, which itself is fainter and less subject to the effects of VNL. We use the {\tt{python}}/{\tt{C++}} code \gs\footnote{\url{https://github.com/GalSim-developers}} \citep{rowe15} to create PSF profiles with the optical properties of \wfa\ to analyze the impact of VNL on PSF size and ellipticity.

In Section \S2 we summarize the main characteristics of the NIR detectors that will be utilized in \wfa\, and discuss about VNL. In Section \S3 we describe the simulations we create to study VNL for \wfa\ PSF profiles. Section \S4 presents our main results on fractional errors in size and absolute errors in ellipticity caused by VNL, as function of relevant parameters such as mean non-linearity amplitude and PSF magnitude. We conclude in Section \S5 with a discussion of our results and how they can be use din the derivation of NIR detector specifications to satisfy WL accuracy requirements.

\section{Voltage non-linearity in the NIR detectors of \wfa}
\label{section:vnl}
%\textcolor{red}{In this section we explain voltage non-linearity, and how it can affect WL science through PSF broadening. Cite the appropriate references from the literature (i.e., previous studies of VNL for these type of detectors). Roger's document on measurements and emails have many good explanations, and should be cited/paraphrased.}

@@

The \wfa\ mission will use a 2.4-m telescope equipped with a Wide Field Instrument (WFI) with 6 bandpass filters (Z087, Y106, J129, W149, H158, and F184 \citep{spergel15})\footnote{In addition to a integral field unit and a coronagraph for supernovae and exoplanet studies, respectively} for constraining dark energy. The WFI will perform a high-latitude survey (HLS) over an area of 2200 deg$^2$ in four NIR ($\sim0.92 - 2.00 \mu$m) bands (Y106, J129, H158, and F184) down to a 5$\sigma$ point-source AB magnitude of 26.7 in J. The weak lensing program in the HSL will measure shapes of about 380 million galaxies in the J129, H158, and F184 \citep{green12,spergel15}

The WFI possesses a wide-field channel that has a Focal Plane Assembly (FCA) of 18 4k x 4k HgCdTe (mercury, cadmium, and telluride, or ``MerCadTel") Sensor Chip Assemblies (SCAs), arranged in a 6x3 layout and with a pixel size and plate scale of 10 $\mu$m and 0.11 arcseconds per pixel, respectively. The HgCdTe NIR detectors are manufactured by Teledyne Imaging Sensors, and are part of a family of detectors known as H4RG\footnote{``HAWAII 4k$\times$4k pixels with Reference pixels and Guide mode", where ``HAWAII" stands for HgCdTe Astronomical Wide Area Infrared Imager}.

@@

The last two types of non-linearity depend on fluence (total flux per pixel, or integrated signal, as opposed to RF, which is flux dependent), and can be analyzed together in a singe transfer function known as \emph{voltage non-linearity} (VNL). We study the impacts of VNL (more relevant at high signals) on PSF measurements in this paper, while we leave investigations on the consequences of RF (relevant at lower signals) on WL measurements for future work.

Laboratory measurements with a H2RG detector (similar to the H4RG that will be used in the WFI) show that the voltage relation for a measured signal S is well fit by a quadratic function in the \emph{average} signal $\langle Q \rangle$ of the form:
\begin{align}
S(\langle Q \rangle)=\langle Q \rangle-\beta \langle Q \rangle^2 \ \ (e^{-})
\label{vnl}
\end{align}
We \emph{assume} that each individual pixel satisfies a VNL function of the same form as Eq. \ref{vnl}, and that the spatial variation on VNL is such as the non-linearity coefficient $\beta$ in each pixel can be drawn from a Normal distribution of the form $\mathcal{N} \sim (\beta_0, 0.12\beta_0)$, where the nominal value $\beta_0 \equiv 3.566\times10^{-7}/e^{-}$ and the dispersion parameter of the distribution (RMS$=0.12\beta_0$). This mean nominal value implies an attenuation of the signal of about $3.5\%$ per each $10^5$ e$^-$ of input signal (Eq. \ref{vnl}). We assume that galaxies will have about two orders of magnitude less total electrons than bright stars, and therefore for this quadratic model, star shapes are distorted by VNL and galaxies are (approximately) not, which would result in incorrect PSF correction if not accounted for.  We have verified that the results using the mean VNL coefficient for all pixels do not differ significatively from those using the distribution above for each pixel.

@@

\section{Methods}
\label{methods}
\subsection {Simulations}
We use the publicly available {\tt{GalSim}} code (v.13) to simulate the impact of VNL on the \wfa\ PSF shape and size. {\tt{GalSim}} is a {\tt{python/C++}} open-source code that allows the user to create simulations of astronomical objects, and it is especially useful in weak lensing investigations.

\citet{kannawadi15} have developed within \gs\ (v1.3) a \wfa\ module called ``{\tt{galsim.wfirst}}", which allows the simulation of a PSF profile according to the optical design characteristics of the \wfa\ WFI \citep{pasquale14})\footnote{\citet{pasquale14} discuss the so-called ``Cycle 4" optical design, whereas the \gs\ \wfa\ module -used in this work- uses files corresponding to ``Cycle 5"}) through the calling of {\tt{galsim.wfirst.getPSF}} routine. This routine returns a {\tt{python}} dictionary of {\tt{galsim.ChromaticOp-}}\\{\tt{ticalPSF}} objects indexed by each one of the 18 H4RG SCAs of the FPA. It uses the optical configuration of the pupil plane to simulate PSF images in any \wfa\ WFI bandpass filter, with expected optical aberrations approximated as a linear combination of Zernike polynomials (up to Noll order equal to $11$, \citet{noll67}). For this work, we have created simulations in the four bands of the HLS (see Table 1).  A central circular obscuration ($30 \%$) and six support struts are included as well. The pupil plane configurations and Zernike models are publicly available.\footnote{\url{http://wfirst.gsfc.nasa.gov/science/sdt_public/wps/references/instrument/}}

The current version of the module does not include PSF variations within the detector, and the PSF returned corresponds to that at the center of the SCA. In addition, the module assumes that the pupil plane configuration of all the six bands is the same and equivalent to that of the ``red" bands (\emph{i.e.}, W149, H158, and F184), and that the struts are not, in general, radial nor evenly spaced. However, these last two assumptions can be relaxed to expedite calculations, and the optional keyword {\tt{approximate\char`_struts}} can be set to {\tt{True}}. The module generates PSF models that do not include pointing jitter nor charge diffusion.

For the simulations in this work, SCA number 18 was selected, which was found to have the largest intrinsic ellipticity (see below for a description of the shape measurement method utilized) across all bands among all the SCAs (Table 1). Aberrations such as defocus, astigmatism, coma, and line-of-sight motion patters couple to propagate into terms that produce azimuthally asymmetrical profiles. We also evaluate the PSF at the mean wavelength weighted by each bandpass or effective wavelength, and set the {\tt{approximate\char`_struts}} keyword to {\tt{False}} when creating the profile. We then form an effective PSF by convolving the profile with a 2D box car profile of length equal to the nominal plate scale of the \wfa\ WFI ({\tt{galsim.wfirst.pixel\char`_ scale$=0.11$}} arcseconds per pixel).

%Table 1
\begin{table}[!htb]
\centering
\begin{tabular}{ |c| c | c| c| c| c| c | c|}
\hline
\multirow{2}{*}{Band} & Min. $\lambda$ & Max. $\lambda$ & $\lambda_{\text{eff}}$ & k($\lambda$) & e$_1$ & e$_2$ & $\sigma$ \\
& ($\mu$m) & ($\mu$m) & ($\mu$m) & (e$^{-}$) &  (SCA$=$18) & (SCA$=$18) & (pix) (SCA$=$18)  \\
\hline 
Y106 & 0.900 & 1.010 & 0.873 & 3.4470$\times10^4$ & 0.00841  & 0.2010 & 4.4455 \\
J129  & 1.095 & 1.500 & 1.292 & 9.5477$\times10^4$  & 0.00793 & 0.1313 & 4.5140 \\
H158 & 1.340 & 1.830 & 1.577 & 9.5178$\times10^4$  & 0.00790 & 0.0807 & 4.8340 \\
F184 & 1.630 & 2.060 & 1.837 & 7.1792$\times10^4$  & 0.00592 & 0.0557 & 5.2781 \\
\hline
\end{tabular}
\caption{The first column lists the four bands that will be used in the HLS. For weak lensing analysis, multi-band shape measurement will be done in J129, H158, and F184. Columns 2, 3, and 4 show their minimum, maximum, and effective wavelengths, respectively (from \citet{kannawadi15}). Column 5 shows the baseline flux (in electrons) $k(\lambda)$ of Eq. \ref{flux} at AB magnitude 20 as calculated by the ETC-WL, using the parameters defined in the Appendix. The last three columns show the ellipticity components and size of the \wfa\ PSF profile in SCA number 18 as calculated by the adaptive moments routine in \gs. SCA 18 was found to possess the largest values of absolute PSF ellipticity.} \label{table:1}
\end{table}

The resulting PSF profile created in this way will be undersampled (in accordance with the \wfa\ WFI design). In order to maximize the field of view, detectors in instruments of space missions are usually built with a physical size that results in undersampled images, which fail to satisfy the Nyquist-Shannon criterium for the maximum band limit set by the optical response of the system, and therefore produce aliased images.\footnote{The Nyquist-Shannon criterium states that the sampling interval $p$ must satisfy $p < 1/(2 u_{max})$, where $u_{max}$ is the highest frequency in the signal, in order to avoid aliasing.} In general, it is not possible to recover all the information of a continuous function from a discrete sample of points if the image is aliased, and measurements of astronomical object's properties such as magnitude and shape will be erroneous \citep{lauer99a,fruchter11,rhodes07}.

To overcome this problem in real data, multiple dithered exposures are taken, and then put together by means of an image combination algorithm \citep{lauer99b,fruchter02,bertin06,rowe11} in order to produce an oversampled image that satisfies the Nyquist-Shannon criterium.

>>>>

\newcommand {\gs} {{\tt{GalSim}}}  
\newcommand {\wf} {WFIRST}  
\newcommand {\wfa} {WFIRST}  
\newcommand {\optical} {{\tt{OpticalPSF}}} 
\newcommand {\gauss} {{\tt{Gaussian}}}

@@

%\title{Voltage non-linearity effects on \wfa\ PSF profiles for weak lensing measurements using {\tt{GalSim}} simulations}
\title{The effect of detector nonlinearity on \wfa\ PSF profiles for weak gravitational lensing measurements}
\author{A. A. Plazas$^{\dagger a}$, C. Shapiro$^{a,b}$, J. Rhodes$^{a,b,c}$, \& R. Smith$^b$}
\email{$^\dagger$andres.a.plazas.malagon@jpl.nasa.gov}
\affil{$^a$Jet Propulsion Laboratory, California Institute of Technology, 4800 Oak Grove Dr., Pasadena, CA 91109, USA}
\affil{$^b$California Institute of Technology, 1200 E. California Blvd, CA 91125, USA}
\affil{$^c$Institute for the Physics and Mathematics of the Universe, 5-1-5 Kashiwanoha, Kashiwa, Chiba Prefecture 277-8583, Japan }
\begin{abstract}
Weak gravitational lensing (WL) is one of the most powerful techniques to learn about the dark sector of the universe. To extract the WL signal from astronomical observations, observed galaxy shapes must be measured and corrected for the Point Spread Function (PSF) of the imaging system with extreme accuracy (of the order of 1 part per 1000 in the fractional and absolute errors in size and ellipticity). Biases in shape measurements can potentially originate in the detectors by any particular instrument. Future missions such as NASA's Wide Field Infrared Survey Telescope-Astrophysics Focused Telescope Asset (\wfa) will use a new family of hybrid near-infrared CMOS detectors (HAWAII-4RG) that are untested for accurate WL measurements. Like any other detector, these devices are intrinsically subject to non-linearities in the conversion of photo-generated charge to measured voltage that tend to attenuate bright objects such as reference stars that are used for PSF determination. In this paper, we study and set preliminary requirements on the impact on \wf\ PSF properties (size and ellipticity) induced by this type of detector non-linearity (NL), setting preliminary requirements We use the publicly-available \gs\ and the \wf\ Exposure Time Calculator codes to generate customized simulations of the PSF optical profiles expected for \wf\ and study the consequences of a one-parameter non-linearity function quadratic in the signal $Q$ (in electrons) per pixel, $f(Q)=Q-\beta Q^2$. We use these simulations to measure the fractional error in the PSF size ($\Delta R/R$) and the absolute error in the PSF ellipticity ($\Delta e$) as a function of parameters such as the expected magnitude of typical stars in \wf\ and  $\beta$. For a nominal $\beta_0=3.566\times10^{-7}/e^{-}$, NL attenuates the signal by $\sim 4\%$ for a pixel full well depth of about $1.1^5$ e$^-$. Since the NL effects depend on PSF size and flux, we find variation in its amplitude among the four bands of the High Latitude Survey (HLS) of \wf\ (being the largest for the J129 band). As $\beta$ is allowed to increase, the values of $\Delta R/R$ and $\Delta e$ increase linearly in all bands at a fixed magnitude. Uncalibrated, NL at its nominal value can induce an error of $\Delta R/R=2.5\times 10^{-3}$ and $\Delta e_2=5\times^{-4}$ in the \wf\ PSF size and ellipticity in the H158 bandpass for the expected brightest stars (AB magnitude of $\sim m=20$) in the HLS of \wf. In addition, our simulations show that to limit the bias of $\Delta R/R$ and $\Delta e$ in the H158 band to better than 1 part in 1000, the mean $\beta$ must be calibrated to $\sim3.5\%$ and $\sim 10\%$, respectively. 
\end{abstract}

\section{Introduction}
Weak gravitational lensing (WL) has been identified as a powerful probe of the nature and evolution of the components of the Universe. In particular, \emph{cosmic shear}-the subtle  distortions of background galaxy shapes by the large scale structure of the Universe-constrains the properties of dark matter and dark energy through the measurement of the expansion history and growth of structure of the Universe \citep{refregier03, hoekstra08, kilbinger15}. WL measurements also allow to test the validity of General Relativity that relates the gravitational potential to the matter-energy distribution. Several visible surveys of $>1000$~deg$^2$ of the sky are currently underway and use the WL signal from hundreds of millions of galaxies as one of their central scientific techniques (\emph{e.g.}, the Dark Energy Survey (DES) \citep{diehl12,jarvis15}, the the Kilo-Degree Survey (KiDS) \citep{kuijken15}, and the Hypersuprime-Camera Survey (HSC)\citep{miyazaki12}. In addition, future ground- and spaced-based surveys and missions in the visible and near infra-red (NIR) are planned to image more than O($10^9$) galaxies in the next decade (\emph{e.g.}, the Large Synoptic Survey Telescope (LSST) \citep{ivezic08}, the Euclid spacecraft \citep{laureijs11} and NASA's planned Wide Field Infrared Survey Telescope (WFIRST) in its Astrophysics Focused Telescope Asset (AFTA) implementation \citep{green12,spergel13,spergel15}).

The process of extracting the WL signal from images of the sky, in the presence of intrinsic galaxy ellipticity variations that are $\sim$ 0.4 r.m.s, is highly non-trivial. It must be done through an statistical analysis of large galaxy samples, with a careful control of systematic uncertainties. The dominant signal produced by WL can be described by a local linear transformation of the source image that produces a shear (a complex, spin-2 field of components $\gamma_1$ and $\gamma_2$) and a scalar magnification, both of which have an r.m.s. amplitude of only $\sim 2 \%$ in the case of cosmic shear. Most of the background galaxies usable by WL are at hight redshift (with low signal-to-noise (S/N) ratio) and with a size comparable or smaller than the Point Spread Function (PSF) of the imaging system. The PSF itself is usually larger than the lensing signal by an order of magnitude, inducing a modulation in the signal (multiplicative errors) and asymmetries that produce coherent spurious patterns (additive errors) that mimmic the WL signal. Bright stars are commonly used to estimate the PSF function, and then this information must be interpolated to the observed galaxy positions to deconvolve the PSF contribution and measure the galaxy shape (in the form of a complex ellipticity $e=e_1 + i e_2$) to estimate the shear field\footnote{Most of the shape measurement algorithms to date rely on the accurate measurements of galaxy shapes to produce an estimator of the WL shear field $(\gamma_1, \gamma_2)$. However, recent algorithms propose skipping this step and creating a direct shear estimator through Bayesian analysis in Fourier space \citep{bernstein14,bernstein15})}. This interpolation step is subject to introduce systematic errors if the information inferred from the stars does not fully constrain the PSF at the galaxy position with the required accuracy.  In order not to bias the determination of cosmological parameters and dark energy, the ellipticity and size of the PSF must be known to an accuracy of O(10$^{-3}$) \citep{huterer06,amara08,paulin08,paulin09,massey13,cropper13} or better ($4.7 \times 10^{-4}$ for the knowledge of the \wfa\ PSF ellipticity  \citep{spergel13}).

@@

Systematic errors that originate from a telescope's detectors (image sensors) can introduce biases in astronomical observables such as photometry and astrometry that propagate into shear measurement biases. These type of errors have been extensively studied in the case of thick, fully-depleted, high-resistivity Charge Coupled-Devices (CCDs), which are the detectors of choice for many current and planned surveys such as DES, HSC, and LSST \citep{stubbs14,plazas14,gruen15}. It is of great importance to qualitatively quantify the impact of these sensor effects on the inference of cosmological parameter, in particular through WL \citep{jarvis14,mandelbaum14b,meyers14}. Future missions such as the James Webb Space Telescope and \wfa\ will utilize a new family of near-infrared detectors that are subject as well to effects such as non-linearity, reciprocity failure \citep{bohlin05,biesiadzinski11}, interpixel capacitance (IPC) \citep{mccullough08,kannawadi15}, and persistence \citep{smith08}, and that can potentially imprint biases on weak lensing shape measurements if not taken into account.

In this paper we study the effect on PSF size and ellipticity of the non-linearity in the conversion of photo-generated charge to measured voltages in the NIR detectors that will be used by NASA's \wfa\ mission. This type of detector non-linearity (NL) will tend to attenuate the measured flux in bright stars, broadening the inferred PSF and complicating its deconvolution from the observed galaxy image, which itself is fainter and less subject to the effects of NL. Our analysis is also useful to set preliminary requirements on NL for these sensors. We use the {\tt{python}}/{\tt{C++}} code \gs\footnote{\url{https://github.com/GalSim-developers}, \url{https://wfirst.ipac.caltech.edu/sims/Code.html}} \citep{rowe15} to create PSF profiles with the optical properties of \wfa\ to analyze the impact of NL on PSF size and ellipticity.

In Section \S2 we summarize the main characteristics of the NIR detectors that will be used in \wfa\, and describe NL. In Section \S3 we describe the simulations we create to study NL for \wfa\ PSF profiles. Section \S4 presents our main results on fractional errors in size and absolute errors in ellipticity caused by NL, as function of relevant parameters such as mean non-linearity amplitude and PSF magnitude. We conclude in Section \S5 with a discussion of our results and how they can be used in the derivation of NIR detector specifications to satisfy WL accuracy requirements.

\section{Voltage non-linearity in the NIR detectors of \wfa}
\label{section:NL}
%\textcolor{red}{In this section we explain voltage non-linearity, and how it can affect WL science through PSF broadening. Cite the appropriate references from the literature (i.e., previous studies of NL for these type of detectors). Roger's document on measurements and emails have many good explanations, and should be cited/paraphrased.}

@@

The \wfa\ mission will use a 2.4-m telescope equipped with a Wide Field Instrument (WFI) with 6 bandpass filters (Z087, Y106, J129, W149, H158, and F184 \citep{spergel15}).\footnote{In addition to a integral field unit and a coronagraph for supernovae and exoplanet studies, respectively} The WFI will perform a high-latitude survey (HLS) over an area of 2200 deg$^2$ in four NIR ($\sim0.92 - 2.00 \mu$m) bands (Y106, J129, H158, and F184) down to a 5$\sigma$ point-source AB magnitude of 26.7 in J. The weak lensing program in the HLS will measure shapes of about 380 million galaxies in the J129, H158, and F184 \citep{green12,spergel15}

The WFI possesses a wide-field channel that has a Focal Plane Assembly (FPA) of 18 4k$\times$4k HgCdTe NIR detectors, arranged in a 6x3 layout and with a pixel size and plate scale of 10 $\mu$m and 0.11 arcseconds per pixel, respectively. The HgCdTe NIR detectors are manufactured by Teledyne Imaging Systems, and are part of a family of detectors known as HXRG\footnote{``HAWAII Xk$\times$Xk pixels with Reference pixels and Guide mode", where ``HAWAII" stands for HgCdTe Astronomical Wide Area Infrared Imager}.

@@

The last two types of non-linearity depend on fluence (total flux per pixel, or integrated signal, as opposed to RF, which is flux dependent), and can be analyzed together in a singe transfer function typically called ``nonlinearity". We study the impacts of NL (more relevant at high signals) on PSF measurements in this paper, while we leave investigations on the consequences of RF (relevant at lower signals) on WL measurements for future work.

Measurements with H2RG 1.7$\mu$m cutoff detectors produced for the NIR channel of the Wide Field Camera 3 (WFC3) installed onboard the Hubble Space Telescope (with the same basic design of the H4RG that will be used in the WFI but with 18 $\mu$m pixels) show that the voltage relation for a measured signal $S$ is well fit by a quadratic function in the \emph{mean} signal $\langle Q \rangle$ of the form:
\begin{align}
S(\langle Q \rangle)=\langle Q \rangle-\beta \langle Q \rangle^2 \ \ (e^{-})
\label{NL}
\end{align}
We \emph{assume} that each individual pixel satisfies a NL function of the same form as Eq. \ref{NL}, and that the spatial variation on NL is such as the non-linearity coefficient $\beta$ in each pixel can be drawn from a Normal distribution of the form $\mathcal{N} \sim (\beta_0, 0.12\beta_0)$, where the nominal value $\beta_0 \equiv 3.566\times10^{-7}/e^{-}$ and the dispersion parameter of the distribution (r.m.s.$=0.12\beta_0$) includes shot noise and deviations of the individual NL curves from the mean NL. This mean nominal value implies an attenuation of the signal of about $4\%$ for a pixel full well depth in the WFI detectors of $1.1 \times 10^5$ electrons \footnote{Dave Content (GSFC), private communication.} (Eq. \ref{NL}). We assume that galaxies will have about two orders of magnitude less total electrons than bright stars, and therefore for this quadratic model, star shapes are distorted by NL and galaxies are (approximately) not, which would result in incorrect PSF correction if not accurately calibrated. We have verified that the results using the mean NL coefficient for all pixels do not differ significatively from those using the distribution above for each pixel.

@@

\section{Methods}
\label{methods}
\subsection {Simulations}
We use the publicly available {\tt{GalSim}} code (v.13) to simulate the impact of NL on the \wfa\ PSF shape and size. {\tt{GalSim}} is a {\tt{python/C++}} open-source code that allows the user to create simulations of astronomical objects, and it is especially useful in weak lensing investigations.

\citet{kannawadi15} have developed within \gs\ (v1.3) a \wfa\ module called ``{\tt{galsim.wfirst}}", which allows the simulation of a PSF profile according to the optical design characteristics of the \wfa\ WFI \citep{pasquale14})\footnote{\citet{pasquale14} discuss the so-called ``Cycle 4" optical design, whereas the \gs\ \wfa\ module -used in this work- uses files corresponding to ``Cycle 5"}) through the calling of {\tt{galsim.wfirst.getPSF}} routine. This routine returns a {\tt{python}} dictionary of {\tt{galsim.ChromaticOp-}}\\{\tt{ticalPSF}} objects indexed by each one of the 18 H4RG detectors of the FPA. It uses the optical configuration of the pupil plane to simulate PSF images in any \wfa\ WFI bandpass filter, with expected optical aberrations approximated as a linear combination of Zernike polynomials (up to Noll order equal to $11$, \citet{noll67}). For this work, we have created simulations in four bands of the HLS (see Table 1).  A central circular obscuration ($30 \%$) and six support struts are included as well. The pupil plane configurations and Zernike models are publicly available.\footnote{\url{http://wfirst.gsfc.nasa.gov/science/sdt_public/wps/references/instrument/}}

The current version of the module does not include PSF variations across the detector field of view, and the PSF returned corresponds to that at its center. In addition, the module assumes that the pupil plane configuration of all the six bands is the same and equivalent to that of the ``red" bands (\emph{i.e.}, W149, H158, and F184), and that the struts are not, in general, radial nor evenly spaced. However, these last two assumptions can be relaxed to expedite calculations, and the optional keyword {\tt{approximate\char`_struts}} can be set to {\tt{True}}. The module generates PSF models that do not include pointing jitter nor charge diffusion. These effects could be added to the profile (\emph{e.g.,} by means of an extra convolution with a Gaussian profile in the case of diffusion), but we did not include them in our simulations. Their effect would be to create a slightly larger PSF, reducing the impact NL. Their omission makes our results slightly conservative.

To make our results conservative, we simulate only detector \#18, whose PSF was determined to have the largest ellipticity (see below for a description of the shape measurement method used) across all bands among all the detectors (Table 1). Aberrations such as defocus, astigmatism, coma, and line-of-sight motion patters couple to propagate into terms that produce azimuthally asymmetrical profiles. We also evaluate the PSF at the mean wavelength weighted by each bandpass or effective wavelength, and set the {\tt{approximate\char`_struts}} keyword to {\tt{False}} when creating the profile. We then form an effective PSF by convolving the profile with a 2D box car profile of length equal to the nominal plate scale of the \wfa\ WFI ({\tt{galsim.wfirst.pixel\char`_ scale$=0.11$}} arcseconds per pixel).

%Table 1
\begin{table}[!htb]
\centering
\begin{tabular}{ |c| c | c| c| c| c| c | c|}
\hline
\multirow{2}{*}{Band} & Min. $\lambda$ & Max. $\lambda$ & $\lambda_{\text{eff}}$ & k($\lambda$) & e$_1$ & e$_2$ & $\sigma$ \\
& ($\mu$m) & ($\mu$m) & ($\mu$m) & (e$^{-}$) &  (chip \#18) & (chip \#18) & (pix) (chip \#18)  \\
\hline 
Y106 & 0.900 & 1.010 & 0.873 & 3.4470$\times10^4$ & 0.00841  & 0.2010 & 4.4455 \\
J129  & 1.095 & 1.500 & 1.292 & 9.5477$\times10^4$  & 0.00793 & 0.1313 & 4.5140 \\
H158 & 1.340 & 1.830 & 1.577 & 9.5178$\times10^4$  & 0.00790 & 0.0807 & 4.8340 \\
F184 & 1.630 & 2.060 & 1.837 & 7.1792$\times10^4$  & 0.00592 & 0.0557 & 5.2781 \\
\hline
\end{tabular}
\caption{The first column lists the four bands that will be used in the HLS. For weak lensing analysis, multi-band shape measurement will be done in J129, H158, and F184. Columns 2, 3, and 4 show their minimum, maximum, and effective wavelengths, respectively (from \citet{kannawadi15}). Column 5 shows the baseline flux (in electrons) $k(\lambda)$ of Eq. \ref{flux} at AB magnitude 20 as calculated by the ETC-WL, using the parameters defined in the Appendix. The last three columns show the ellipticity components and size of the \wfa\ PSF profile in detector number 18 as calculated by the adaptive moments routine in \gs. chip 18 was found to possess the largest values of absolute PSF ellipticity.} \label{table:1}
\end{table}

The resulting PSF profile created in this way will be undersampled (in accordance with the \wfa\ WFI design). In order to maximize the field of view, detectors in instruments of space missions are usually built with a physical size that results in undersampled images, which fail to satisfy the Nyquist-Shannon criterium for the maximum band limit set by the optical response of the system, and therefore produce aliased images.\footnote{The Nyquist-Shannon criterium states that the sampling interval $p$ must satisfy $p < 1/(2 u_{max})$, where $u_{max}$ is the highest frequency in the signal, in order to avoid aliasing.} In general, it is not possible to recover all the information of a continuous function from a discrete sample of points if the image is aliased, and measurements of astronomical object's properties such as magnitude and shape will be erroneous \citep{lauer99a,fruchter11,rhodes07}. Also, in particular, we found that our shape measurement algorithm fails when most light is concentrated in a few pixels.
